\begin{thebibliography}{11}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[Ackerman(2011)]{ackerman_intelligence_2011}
P.~L. Ackerman.
\newblock Intelligence and {Expertise}.
\newblock In R.~J. Sternberg and S.~B. Kaufman, editors, \emph{The {Cambridge}
  {Handbook} of {Intelligence}}, pages 847--860. Cambridge University Press,
  Cambridge, 2011.
\newblock ISBN 978-0-511-97724-4.
\newblock URL
  \url{http://www.cambridge.org/us/academic/subjects/psychology/cognition/cambridge-handbook-intelligence}.

\bibitem[Davidson and Kemp(2011)]{davidson_contemporary_2011}
J.~E. Davidson and I.~A. Kemp.
\newblock Contemporary {Models} of {Intelligence}.
\newblock In R.~J. Sternberg and S.~B. Kaufman, editors, \emph{The {Cambridge}
  {Handbook} of {Intelligence}}, pages 58--82. Cambridge University Press,
  Cambridge, 2011.
\newblock ISBN 978-0-511-97724-4.
\newblock URL
  \url{http://www.cambridge.org/us/academic/subjects/psychology/cognition/cambridge-handbook-intelligence}.

\bibitem[Ericsson(2006)]{ericsson_introduction_2006}
K.~A. Ericsson.
\newblock An {Introduction} to {Cambridge} {Handbook} of {Expertise} and
  {Expert} {Performance}: {Its} {Development}, {Organization}, and {Content}.
\newblock In K.~A. Ericsson, N.~Charness, P.~J. Feltovich, and R.~R. Hoffman,
  editors, \emph{The {Cambridge} handbook of expertise and expert performance},
  pages 3--19. Cambridge University Press, New York, NY, US, 2006.
\newblock ISBN 0-521-60081-2 (Paperback); 0-521-84097-X (Hardcover);
  978-0-521-60081-1 (Paperback); 978-0-521-84097-2 (Hardcover).

\bibitem[Franklin(2014)]{franklin_history_2014}
S.~Franklin.
\newblock History, motivations, and core themes.
\newblock In K.~Frankish and W.~M. Ramsey, editors, \emph{The {Cambridge}
  handbook of artificial intelligence}, pages 15--33. Cambridge University
  Press, Cambridge, UK, 2014.
\newblock ISBN 978-0-521-87142-6.

\bibitem[Gottfredson(1997)]{gottfredson_mainstream_1997}
L.~S. Gottfredson.
\newblock Mainstream science on intelligence: {An} editorial with 52
  signatories, history, and bibliography.
\newblock \emph{Intelligence}, 24\penalty0 (1):\penalty0 13--23, Jan. 1997.
\newblock ISSN 01602896.
\newblock \doi{10.1016/S0160-2896(97)90011-8}.
\newblock URL
  \url{http://linkinghub.elsevier.com/retrieve/pii/S0160289697900118}.

\bibitem[Legg and Hutter(2007{\natexlab{a}})]{legg_collection_2007}
S.~Legg and M.~Hutter.
\newblock A {Collection} of {Definitions} of {Intelligence}.
\newblock In B.~Goertzel and P.~Wang, editors, \emph{Advances in artificial
  general intelligence: concepts, architectures and algorithms: proceedings of
  the {AGI} {Workshop} 2006}, number v. 157 in Frontiers in artificial
  intelligence and applications. IOS Press, Amsterdam ; Washington, DC,
  2007{\natexlab{a}}.
\newblock ISBN 978-1-58603-758-1.

\bibitem[Legg and Hutter(2007{\natexlab{b}})]{legg_universal_2007}
S.~Legg and M.~Hutter.
\newblock Universal {Intelligence}: {A} {Definition} of {Machine}
  {Intelligence}.
\newblock \emph{Minds and Machines}, 17\penalty0 (4):\penalty0 391--444, Nov.
  2007{\natexlab{b}}.
\newblock ISSN 0924-6495, 1572-8641.
\newblock \doi{10.1007/s11023-007-9079-x}.
\newblock URL \url{http://link.springer.com/10.1007/s11023-007-9079-x}.

\bibitem[Mackintosh(2011)]{mackintosh_history_2011}
N.~J. Mackintosh.
\newblock History of {Theories} and {Measurement} of {Intelligence}.
\newblock In R.~J. Sternberg and S.~B. Kaufman, editors, \emph{The {Cambridge}
  {Handbook} of {Intelligence}}, pages 3--19. Cambridge University Press,
  Cambridge, 2011.
\newblock ISBN 978-0-511-97724-4.
\newblock URL
  \url{http://www.cambridge.org/us/academic/subjects/psychology/cognition/cambridge-handbook-intelligence}.

\bibitem[Muehlhauser(2013)]{muehlhauser_what_2013}
L.~Muehlhauser.
\newblock What is {Intelligence}?, June 2013.
\newblock URL
  \url{https://intelligence.org/2013/06/19/what-is-intelligence-2/}.

\bibitem[Urbina(2011)]{urbina_tests_2011}
S.~Urbina.
\newblock Tests of {Intelligence}.
\newblock In R.~J. Sternberg and S.~B. Kaufman, editors, \emph{The {Cambridge}
  {Handbook} of {Intelligence}}, pages 20--38. Cambridge University Press,
  Cambridge, 2011.
\newblock ISBN 978-0-511-97724-4.
\newblock URL
  \url{http://www.cambridge.org/us/academic/subjects/psychology/cognition/cambridge-handbook-intelligence}.

\bibitem[Willis et~al.(2011)Willis, Dumont, and
  Kaufman]{willis_factor-analytic_2011}
J.~O. Willis, R.~Dumont, and A.~S. Kaufman.
\newblock Factor-{Analytic} {Models} of {Intelligence}.
\newblock In R.~J. Sternberg and S.~B. Kaufman, editors, \emph{The {Cambridge}
  {Handbook} of {Intelligence}}, pages 39--57. Cambridge University Press,
  Cambridge, 2011.
\newblock ISBN 978-0-511-97724-4.
\newblock URL
  \url{http://www.cambridge.org/us/academic/subjects/psychology/cognition/cambridge-handbook-intelligence}.

\end{thebibliography}
